FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-20 NewVersion/sections/RelatedWork.tex
Polish

\subsection{Resolving Unintentional Method Conflicts}\label{subsec:middleman}
A few language implementations have realized the problem of
unintentional conflicts and provided some support for it.

@@

\noindent {\bf C++ model.}
C++ supports a very flexible inheritance model (including basic and
virtual inheritance). \bruno{what is ``normal'' inheritance?}\yanlin{changed "normal" to "basic", is this ok?}
C++ allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 
With virtual methods, dynamic dispatch is used and 
method lookup algorithm will find the most specific method definition.
A contribution of our work is to provide a minimal formal model of
hierarchical dispatching, whereas C++ can be viewed as a real-world
implementation. As far as we know there is no any formal model that
captures this aspect of the C++ method dispatching model. Apart from this, as discussed in Section~\ref{subsec:loosen}, \name{} conservatively rejects some interface/class definitions that C++ accepts, and upcasts are never rejected since they are used for ambiguity resolution.
\bruno{The discussion points out further differences. We need to refer
to that discussion here too.}\yanlin{added.}

>>>>

\subsection{Resolving Unintentional Method Conflicts}\label{subsec:middleman}
A few language implementations have realized the problem of
unintentional conflicts and provide some support for it.

@@

\noindent {\bf C++ model.}
C++ supports a very flexible inheritance model.
C++ allows the existence of unintentional conflicts and users may specify a hierarchical path via casts for disambiguation, as discussed in Section~\ref{sec:overview}. 
With virtual methods, dynamic dispatch is used and 
method lookup algorithm will find the most specific method definition.
A contribution of our work is to provide a minimal formal model of
hierarchical dispatching, whereas C++ can be viewed as a real-world
implementation. As far as we know there is no any formal model that
captures this aspect of the C++ method dispatching model. Apart from this, as discussed in Section~\ref{subsec:loosen}, \name{} conservatively rejects some interface/class definitions that C++ accepts, and upcasts are never rejected since they are used for ambiguity resolution.
\bruno{The discussion points out further differences. We need to refer
to that discussion here too.}\yanlin{added.}
